Spatial distribution of environmental DNA in a nearshore marine habitat

### 2017-01-19 Manuscript/v1.2_PeerJ/carkeek_grid.tex
make editorial changes

\subsection*{Objective 2: Spatial distribution of diversity}
\subsubsection*{Community Classification}
To determine the spatial distribution and variation of eDNA communities (objective 2), we used multivariate classification algorithms. We simultaneously assessed the existence of distinct community types and the membership of samples to those community types using an unsupervised classification algorithm known as partitioning around medoids (PAM; sometimes referred to as k-medoids clustering) \citep{Kaufman1990}, as implemented in the R package cluster \citep{cluster}. The classification of samples to communities was made on the basis of their pairwise Bray-Curtis similarity, calculated using the function vegdist in the R package vegan \citep{vegan}. Other distance metrics were evaluated but had no appreciable effect on the outcome of the analysis (Figure \ref{distance_decay_multi}). In order to chose an optimal number of clusters ($K$), we evaluated the distribution of silhouette widths, a measure of the similarity between each sample and its cluster compared to its similarity to other clusters. We repeated the analysis using fuzzy clustering (FANNY, \citep{Kaufman1990}; however, the results were qualitatively similar to the results using PAM so we omit them here.

@@

%-----------------------------------FUNDING-------------------------------------
\section*{Funding}
This work was supported by a grant from the David and Lucile Packard Foundation to RPK (grant 2014-39827). The funders had no role in study design, data collection and analysis, decision to publish, or preparation of the manuscript.

%--------------------------------CONTRIBUTIONS----------------------------------
\section*{Author Contributions}
Conceived and designed the experiments:
JL O'Donnell, RP Kelly, AO Shelton;
Collected the data:
JL O'Donnell, NC Lowell, GD Williams, RP Kelly, AO Shelton, JF Samhouri;
Conducted the analyses:
JL O'Donnell;
Wrote the first draft:
JL O'Donnell;
Edited the manuscript:
JL O'Donnell, AO Shelton, RP Kelly, JF Samhouri, GD Williams, NC Lowell

%-----------------------------------ETHICS--------------------------------------
\section*{Ethics Statement}
The authors declare no conflict of interest.
Consistent with the public trust doctrine, waters of the US are public, and therefore no permit was necessary to conduct this research (see Illinois Central Railroad v. Illinois, 146 U.S. 387 (1892)).

>>>>

\subsection*{Objective 2: Spatial distribution of diversity}
\subsubsection*{Community Classification}
To determine the spatial distribution and variation of eDNA communities (objective 2), we used multivariate classification algorithms. We simultaneously assessed the existence of distinct community types and the membership of samples to those community types using an unsupervised classification algorithm known as partitioning around medoids (PAM; sometimes referred to as k-medoids clustering) \citep{Kaufman1990}, as implemented in the R package cluster \citep{cluster}. The classification of samples to communities was made on the basis of their pairwise Bray-Curtis similarity, calculated using the function vegdist in the R package vegan \citep{vegan}. Other distance metrics were evaluated but had no appreciable effect on the outcome of the analysis (Supplemental Figure \ref{distance_decay_multi}). In order to chose an optimal number of clusters ($K$), we evaluated the distribution of silhouette widths, a measure of the similarity between each sample and its cluster compared to its similarity to other clusters. We repeated the analysis using fuzzy clustering (FANNY, \citep{Kaufman1990}; however, the results were qualitatively similar to the results using PAM so we omit them here.

@@

%-----------------------------------FUNDING-------------------------------------
% \section*{Funding}
% This work was supported by a grant from the David and Lucile Packard Foundation to RPK (grant 2014-39827). The funders had no role in study design, data collection and analysis, decision to publish, or preparation of the manuscript.
%
%--------------------------------CONTRIBUTIONS----------------------------------
% \section*{Author Contributions}
% Conceived and designed the experiments:
% JL O'Donnell, RP Kelly, AO Shelton;
% Collected the data:
% JL O'Donnell, NC Lowell, GD Williams, RP Kelly, AO Shelton, JF Samhouri;
% Conducted the analyses:
% JL O'Donnell;
% Wrote the first draft:
% JL O'Donnell;
% Edited the manuscript:
% JL O'Donnell, AO Shelton, RP Kelly, JF Samhouri, GD Williams, NC Lowell

%-----------------------------------ETHICS--------------------------------------
% \section*{Ethics Statement}
% The authors declare no conflict of interest.
% Consistent with the public trust doctrine, waters of the US are public, and therefore no permit was necessary to conduct this research (see Illinois Central Railroad v. Illinois, 146 U.S. 387 (1892)).
